---
title: "Analysis of SARS-CoV-2 SNP Data"
author: "Anthony Kessell"
date: "September 23, 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```


# Load packages and Data

We are going to load both the dplyer and ggplot2 packages for our analysis.

```{r, load-packages-and-data}
library(dplyr)
library(ggplot2)
library(knitr)

# load in SNP data
snp_data <- read.csv("data/sample_snp_data.csv")
```

The first question we have about this dataset is the quality of the SNP calls for each of the three different samples in this dataset. To asses this we'll take a look at the mean and standard deviation of the quality scores in the dataset.

```{r, summarize-quality}
snp_data %>%
  group_by(sample) %>%
  summarise(mean_quality = mean(qual),
            sd_quality = sd(qual)) %>%
  kable()
```

From this, we can see that sample SRR12433065 

To dig in a bit here, let's ,ales a plot looking at the distribution of SNPs across the genome for these three samples to see if there is some pattern. Maybe all the low quality ones are in a specific region.

```{r, plot-quality-across-genome}
snp_data %>%
  ggplot(aes(x = pos,
           y = qual,
           color = sample)) +
  geom_point(size = 3) +
  labs(title = "SNP quality across SARS-CoV-2 Genome",
       x = "Position in Genome (nt)",
       y = "SNP Quality")
```






